### 2015-11-18 Thesis Draft Tianpei Chen/Thesis Draft/C-GA.tex
test the uniform dual objective function optimization

\chapter{Low Complexity Near Optimal Hybrid Detector based on Genetic Algorithm}
In the previous chapter, we introduce two CSVPD aided local search based algorithms, and show the improvement CSVD-LAS -OPIC comparing to MMSE-LAS -OPIC.    
a current trend is the hybridization of of single solution based metaheuristics algorithms in population-based ones, working as intelligent subordinate heuristic operators. In this chapter, we introduce Hybrid Genetic Algorithms which utilizes OPIC as a genetic operator and accelerate the revolution process comparing to random revolution, in addition the performance of the proposed algorithm can be further improved by the hybridization with the principle from neighbour variable search. 
\section{Genetic Algorithm}

>>>>

\chapter{Low Complexity Near Optimal Hybrid Detector based on Genetic Algorithm}\label{Chapter GA}
In the previous chapter, we introduce two CSVPD aided local search based algorithms, and show the improvement CSVD-LAS -OPIC comparing to MMSE-LAS -OPIC.    
a current trend is the hybridization of of single solution based metaheuristics algorithms in population-based ones, working as intelligent subordinate heuristic operators. In this chapter, we introduce Hybrid Genetic Algorithms which utilizes OPIC as a genetic operator and accelerate the revolution process comparing to random revolution. Furthermore, instead of randomly generated initial population, the solution of the CSVPD is fed to Hybrid GA and the initial generation consists of the neighbour of the initial solution from CSVPD.  
\section{CSVPD aided Hybrid Genetic Algorithm}
Genetic Algorithm (GA) is one of the population-based metaheuristic algorithms and can be viewed as a computational model of natural biological evolution process. GA works iteratively and in each iteration it handles a fixed size population of individuals. A number of intelligent genetic operators are used to update the population. Usually the individuals are a string of symbols that represent a candidate solution to the problems. GA has been applied in Code Division Multiple Access (CDMA) detection problem\cite{juntti1997genetic}\cite{ergun2000multiuser}.

Figure (\ref{}) shows the flow chart of the proposed hybrid GA. In the beginning, the initial solution of CSVPD is fed to GA, a initial population of solutions are generated based on this initial solution, then in each iteration, each candidate solution is evaluated and selected by fitness function. The elites are selected as parents which can generate offspring. The offsprings are generated by recombining a pair of parents, this process is called crossover. Then mutation operates to offsprings with a given possibility. OPIC is integrated in GA as an operator that can accelerate the process that GA approximate to optimal solution. The populations is finally reconstructed by the parents and their offsprings. The best solution is chosen when the stopping criteria satisfied.

\subsection{Initialization}
\subsection{Selection}
\subsection{Mutation}
\subsection{OPIC} 
\subsection{Stopping Criteria}

### 2015-11-18 Thesis Draft Tianpei Chen/Thesis Draft/C-Intro.tex
test the uniform dual objective function optimization

%Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}. 
Besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a variety of metaheuristic based local search algorithms invoked from machine learning field\cite{chockalingam2010low} have been proposed for large MIMO systems. These algorithms have complexities that are comparable or slightly higher comparing to MMSE detector and near-optimal performance. Such algorithms include likelihood ascend searching (LAS) algorithm and variants\cite{vardhan2008low}\cite{cerato2009hardware}\cite{li2010multiple} %An theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was also presented\cite{sunfamily}.
and Reactive Tabu search (RTS) algorithms and variants
%which have superior performances compared to LAS detectors because of the efficient local minima exit strategy 
(e.g. Layered Tabu search (LTS)\cite{srinidhi2011layered}, Random Restart Reactive Tabu search (R3TS)\cite{datta2010random}). Additionally, there are other algorithms proposed for large MIMO systems including Message passing technique based algorithms (e.g. Belief propagation (BP) detectors based on graphic model and Gaussian Approximation (GA)\cite{som2011low}\cite{som2010improved}\cite{narasimhan2014channel}\cite{goldberger2011mimo}), Probabilistic Data Association (PDA) based algorithms \cite{mohammed2009low}, Monte Carlo sampling technique based algorithms (e.g. Multiple Restart- Mixed Gibbs Sampling (MR-MGS) algorithm\cite{datta2013novel}) and Element based Lattice Reduction (LR) aided algorithms\cite{zhou2013element}.

>>>>

%Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}. 
The key challenge in designing Large-Scale MIMO (LS-MIMO) detectors is to reduce complexities while maintaining high performances. Given the redundant diversity gain potential provided by LS-MIMO\cite{oestges2010mimo} that can only be achieved at very high Signal to Noise Ratio (SNR), one may consider to sacrifice the redundant diversity gains in order to reduce complexities. Furthermore, the ML criterion of MIMO detection stated in (\ref{MLD}) indicates MIMO detection can be naturally classified as a Combinatorial Optimization (CO) problem, that consist of the search for the optimal solution in a discrete and finite set.

Based on the aforementioned situations, the metaheuristics algorithmic frameworks are of intense research interest in LS-MIMO detection in recent years. Metaheuristics refer to the high level algorithmic strategies that guide subordinate heuristics iteratively by combining different intelligent learning operations. Metaheuristics can explore and exploit the searching space efficiently and find near optimal solutions without costing high complexities. The class of algorithms includes but not restrict to Iterative Local Search (ILS), Tabu Search (TS), Simulated Annealing (SA), Genetic Algorithms (GA) and Ant Colony Optimization (ACO).

Therefore besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a variety of metaheuristic based local search algorithms invoked from machine learning field\cite{chockalingam2010low} have been proposed for LS-MIMO systems. These algorithms have complexities that are comparable or slightly higher comparing to MMSE detector and near-optimal performance. Such algorithms include likelihood ascend searching (LAS) algorithm and variants\cite{vardhan2008low}\cite{cerato2009hardware}\cite{li2010multiple} %An theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was also presented\cite{sunfamily}.
and Reactive Tabu search (RTS) algorithms and variants
%which have superior performances compared to LAS detectors because of the efficient local minima exit strategy 
(e.g. Layered Tabu search (LTS)\cite{srinidhi2011layered}, Random Restart Reactive Tabu search (R3TS)\cite{datta2010random}). Additionally, there are other algorithms proposed for large MIMO systems including Message passing technique based algorithms (e.g. Belief propagation (BP) detectors based on graphic model and Gaussian Approximation (GA)\cite{som2011low}\cite{som2010improved}\cite{narasimhan2014channel}\cite{goldberger2011mimo}), Probabilistic Data Association (PDA) based algorithms \cite{mohammed2009low}, Monte Carlo sampling technique based algorithms (e.g. Multiple Restart- Mixed Gibbs Sampling (MR-MGS) algorithm\cite{datta2013novel}) and Element based Lattice Reduction (LR) aided algorithms\cite{zhou2013element}.
